Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2017-02-13 inst/examples/20170201-manuscript.Rmd
kuvien viilaus

```{r 201606krakow-init2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
# Full combined catalogue (Fen + Kun) with marked duplicates
df.combined.preprocessed <- readRDS("df.combined.Rds")
# Data with duplicates removed
df.full <- df.combined.preprocessed %>% filter(!remove)
# Data with years limited as well
df0 <- df.full %>% filter(publication_year >= min.year & publication_year <= max.year)
df0$title_length <- nchar(df0$title)
```

@@

```{r, message=FALSE, warning=FALSE, fig.width=10, fig.height=4, echo=FALSE}
library(dplyr)
library(ggplot2)
theme_set(theme_bw(20))
df <- df0 %>% filter(publication_year >=1640 & publication_year <=1828) %>% group_by(catalog, publication_decade) %>% tally()
p <- ggplot(df, aes(x = publication_decade, y = n, shape = catalog, linetype = catalog)) + 
       geom_point(size = 4) + 
       geom_line(size = 1) + 
       ylab("Documents (n)") + xlab("Publication year") +
       scale_color_manual(values = c("blue", "darkgreen")) + 
       guides(shape = guide_legend(title = "Catalog")) +
       guides(linetype = guide_legend(title = "Catalog")) +       
       ggtitle("Title count")
print(p)
```

@@

```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=7, fig.height=4, fig.show="hold", out.width="400px"}
for (catal in unique(df0$catalog)) {
  df2 <- subset(df0, catalog == catal) %>% group_by(publication_decade, gatherings) %>% summarize(paper = sum(paper, na.rm = TRUE), n = n()) 
  df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))
  df2$highlight <- rep("Other", nrow(df2))
  df2$highlight[df2$gatherings == "8vo"] <- "Octavo"

  p <- ggplot(df2, aes(y = paper,
                       x = publication_decade,
  	       shape = gatherings,
		       linetype = gatherings))		       
  p <- p + geom_point(size = 4)
  p <- p + geom_smooth(method = "loess", size = 1,
         aes(color = highlight, fill = highlight))
  p <- p + scale_color_manual(values = c("darkgreen", "darkgray"))
  p <- p + scale_fill_manual(values = c("darkgreen", "darkgray"))  	 
  p <- p + ggtitle("Paper consumption in time by gatherings")
  p <- p + xlab("Year")
  p <- p + ylab("Paper consumption")
  p <- p + ylim(c(0, max(na.omit(df2$paper))))
  p <- p + guides(linetype = guide_legend(keywidth = 5, title = "Gatherings"),
       	          shape = guide_legend(keywidth = 5, title = "Gatherings"),
       	          fill = "none", # guide_legend(title = "Gatherings"),
       	          color = "none" # guide_legend(title = "Gatherings")
		  )
  p <- p + ggtitle(catal)
  print(p)
}
```

@@

# Calculate title length (word count)
dfo$title_wordcount <- sapply(strsplit(as.character(dfo$title), " "), length)
dfo$title_wordcount[is.na(dfo$title)] <- NA

@@

df <- dfo %>% filter(language %in% top.language) %>%
              group_by(publication_decade, language) %>%
              summarize(mean_title_length = mean(title_wordcount),
	      		n = n())

p <- ggplot(df, aes(x = publication_decade, y = mean_title_length)) +
       geom_point(aes(size = n, shape = language), size = 3) +
       geom_line(aes(linetype = language), size = 1) +
       guides(
            shape = guide_legend(title = "Language"),
            linetype = guide_legend(title = "Language")
	    ) +
       ylab("Title length (word count)") +
       xlab("Publication decade") +
       ggtitle("Title length")

@@

# Add indicator of the publication period
df$period <- cut(df$publication_year,
           breaks = c(1757, 1766, 1775, 1783),
		 include.lowest = TRUE,
		 right = FALSE
		 )

@@

### Fig. 7: Riksdagar: Kungliga

@@

minyear <- 1700
maxyear <- 1800
catal <- "Kungliga"

@@

  df <- subset(dfsel, publication_year >= 1700 & publication_year < 1831 )

@@

  p <- p + geom_line(data = dfm, aes(x = date, y = Documents), col = "black")
  p <- p + geom_point(data = dfm, aes(x = date, y = Documents), col = "black")
  p <- p + scale_x_continuous(breaks=seq(min(dfm$date), max(dfm$date), 10))
  p <- p + ggtitle("Publishing activity")
  p <- p + ylab("Documents / Year")
  p <- p + xlab("Year")
  p <- p + ggtitle(catal)
  print(p)

@@

### Fig. 8: Riksdagar: Fennica

@@

  p <- p + geom_line(data = dfm, aes(x = date, y = Documents), col = "black")
  p <- p + geom_point(data = dfm, aes(x = date, y = Documents), col = "black")
  p <- p + scale_x_continuous(breaks=seq(min(dfm$date), max(dfm$date), 10))
  p <- p + ggtitle("Publishing activity")
  p <- p + ylab("Documents / Year")
  p <- p + xlab("Year")
  p <- p + ggtitle(paste(catal))
  p <- p + xlim(c(minyear, maxyear))
  print(p)
```

@@

```{r octavo2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
# Take cities from Kungliga except Turku
cat <- "Kungliga"
df1 <- df0 %>% filter(publication_place %in% setdiff(cities, "Turku")) %>%
      	       filter(catalog == cat & gatherings == "8vo") %>%
	       group_by(publication_decade, publication_place) %>%
	       summarise(n = n(), paper = sum(paper, na.rm = TRUE), 
	         mean_title_length = mean(title_length, na.rm = TRUE))

# Take cities from Fennica for Turku
cat <- "Fennica"
df2 <- df0 %>% filter(publication_place %in% "Turku") %>%
      	       filter(catalog == cat & gatherings == "8vo") %>%
	       group_by(publication_decade, publication_place) %>%
	       summarise(n = n(), paper = sum(paper, na.rm = TRUE), 
                 mean_title_length = mean(title_length, na.rm = TRUE))

@@

p <- ggplot(df, aes(x = publication_decade, y = mean_title_length)) +
       geom_line(aes(linetype = publication_place), size = 1) +
       geom_point(aes(shape = publication_place), size = 5) +
       xlab("Publication year") +
       ylab("Title length (characters)") +
       ggtitle("Mean title length") +
       guides(shape = guide_legend(title = "Place")) +
       guides(linetype= guide_legend(title = "Place"))        
print(p)
```

@@

  # PAPER CONSUMPTION
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(shape = language), size = 5) +
       geom_line(aes(linetype = language), size = 1) +       
       xlab("Publication year") +
       ylab("Paper consumption") +
       guides(shape = guide_legend(title = "Language")) +
       guides(linetype = guide_legend(title = "Language")) + 
       ggtitle(paste("Temporary Sermons (", catalogue, ")", sep = ""))
  print(p)
```

@@

  # PAPER CONSUMPTION
  theme_set(theme_bw(20))
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(shape = language), size = 5) +
       geom_line(aes(linetype = language)) +       
       xlab("Publication year") +
       ylab("Paper consumption") +
       guides(shape = guide_legend(title = "Language")) +
       guides(linetype = guide_legend(title = "Language")) +        
       ggtitle(paste("Devotional Literature (", catalogue, ")", sep = ""))
  print(p)
```

>>>>

```{r 201606krakow-init2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
# Full combined catalogue (Fen + Kun) with marked duplicates
df.combined.preprocessed <- readRDS("df.combined.Rds")
# Data with duplicates removed
df.full <- df.combined.preprocessed %>% filter(!remove)
# Data with years limited as well
df0 <- df.full %>% filter(publication_year >= min.year & publication_year <= max.year)
# Calculate title length (nchar and word count)
df0$title_length_nchar <- nchar(df0$title)
df0$title_length_wordcount <- sapply(strsplit(df0$title, " "), length)
df0$title_length_wordcount[is.na(df0$title)] <- NA
```

@@

```{r, message=FALSE, warning=FALSE, fig.width=10, fig.height=4, echo=FALSE}
library(dplyr)
library(ggplot2)
theme_set(theme_bw(20))
df <- df0 %>% filter(publication_year >=1640 & publication_year <=1828) %>% group_by(catalog, publication_decade) %>% tally()
p <- ggplot(df, aes(x = publication_decade, y = n, shape = catalog, linetype = catalog)) + 
       geom_point(size = 4) + 
       geom_line(size = 1) + 
       ylab("Documents (n)") + xlab("Publication year") +
       scale_color_manual(values = c("blue", "darkgreen")) +
       guides(shape = guide_legend(title = "Catalog", reverse = TRUE)) +
       guides(linetype = guide_legend(title = "Catalog", reverse = TRUE)) +  
       ggtitle("Title count")
print(p)
```

@@

```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=9, fig.height=4, fig.show="hold", out.width="400px"}
for (catal in unique(df0$catalog)) {
  df2 <- subset(df0, catalog == catal) %>% group_by(publication_decade, gatherings) %>% summarize(paper = sum(paper, na.rm = TRUE), n = n()) 
  df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))
  df2$highlight <- rep("Other", nrow(df2))
  df2$highlight[df2$gatherings == "8vo"] <- "Octavo"
  df2$gatherings <- factor(df2$gatherings, levels = levels(df0$gatherings))

  p <- ggplot(df2, aes(y = paper,
                       x = publication_decade,
  	       shape = gatherings,
		       linetype = gatherings))		       
  p <- p + geom_point(size = 4)
  p <- p + geom_smooth(method = "loess", size = 1,
         aes(color = highlight, fill = highlight))
  p <- p + scale_color_manual(values = c("darkgreen", "darkgray"))
  p <- p + scale_fill_manual(values = c("darkgreen", "darkgray"))  	 
  p <- p + ggtitle("Paper consumption in time by gatherings")
  p <- p + xlab("Year")
  p <- p + ylab("Paper (sheets)")
  p <- p + ylim(c(0, max(na.omit(df2$paper))))
  p <- p + guides(linetype = guide_legend(keywidth = 5, title = "Gatherings"),
       	          shape = guide_legend(keywidth = 5, title = "Gatherings"),
       	          fill = "none", # guide_legend(title = "Gatherings"),
       	          color = "none" # guide_legend(title = "Gatherings")
		  )
  p <- p + ggtitle(catal)
  print(p)
}
```

@@

@@

df <- dfo %>% filter(language %in% top.language) %>%
              group_by(publication_decade, language) %>%
              summarize(mean_title_length = mean(title_length_wordcount),
	      		n = n())

p <- ggplot(df, aes(x = publication_decade, y = mean_title_length)) +
       geom_point(aes(size = n, shape = language), size = 5) +
       geom_line(aes(linetype = language), size = 1) +
       guides(
            shape = guide_legend(title = "Language"),
            linetype = guide_legend(title = "Language")
	    ) +
       ylab("Title length (word count)") +
       xlab("Publication decade") +
       ggtitle("Title length")

@@

# Add indicator of the publication period
df$period <- cut(df$publication_year,
           breaks = c(1757, 1766, 1775, 1783),
		 include.lowest = TRUE,
		 right = FALSE
		 )
df$period <- gsub("\\[", "", df$period)
df$period <- gsub("\\)", "", df$period)
df$period <- gsub(",", ",", df$period)

@@

### Fig. 7: Publishing activity and riksdagar: Kungliga

@@

minyear <- 1700
maxyear <- 1830
catal <- "Kungliga"

@@

  df <- subset(dfsel, publication_year >= minyear & publication_year <= maxyear)

@@

  p <- p + geom_line(data = dfm, aes(x = date, y = Documents), col = "black")
  p <- p + geom_point(data = dfm, aes(x = date, y = Documents), col = "black")
  p <- p + scale_x_continuous(breaks=seq(min(dfm$date), max(dfm$date), 10))
  p <- p + ylab("Title count (n)")
  p <- p + xlab("Year")
  p <- p + ggtitle(paste(catal, " ", minyear, "-", maxyear, sep = ""))
  print(p)
```

@@

### Fig. 8: Publishing activity and riksdagar: Fennica

@@

  p <- p + geom_line(data = dfm, aes(x = date, y = Documents), col = "black")
  p <- p + geom_point(data = dfm, aes(x = date, y = Documents), col = "black")
  p <- p + scale_x_continuous(breaks=seq(min(dfm$date), max(dfm$date), 10))
  p <- p + ylab("Title count (n)")
  p <- p + xlab("Year")
  p <- p + ggtitle(paste(catal, " ", minyear, "-", maxyear, sep = ""))  
  p <- p + xlim(c(minyear, maxyear))
  print(p)
```

@@

```{r octavo2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
# Take cities from Kungliga except Turku
cat <- "Kungliga"
df1 <- df0 %>% filter(publication_place %in% setdiff(cities, "Turku")) %>%
      	       filter(catalog == cat & gatherings == "8vo") %>%
	       group_by(publication_decade, publication_place) %>%
	       summarise(n = n(), paper = sum(paper, na.rm = TRUE), 
	         mean_title_length = mean(title_length_wordcount, na.rm = TRUE))

# Take cities from Fennica for Turku
cat <- "Fennica"
df2 <- df0 %>% filter(publication_place %in% "Turku") %>%
      	       filter(catalog == cat & gatherings == "8vo") %>%
	       group_by(publication_decade, publication_place) %>%
	       summarise(n = n(), paper = sum(paper, na.rm = TRUE), 
                 mean_title_length = mean(title_length_wordcount, na.rm = TRUE))

@@

p <- ggplot(df, aes(x = publication_decade, y = mean_title_length)) +
       geom_line(aes(linetype = publication_place), size = 1) +
       geom_point(aes(shape = publication_place), size = 5) +
       xlab("Publication year") +
       ylab("Title length (characters)") +
       ggtitle("Octavo: mean title length") +
       guides(shape = guide_legend(title = "Place")) +
       guides(linetype= guide_legend(title = "Place"))        
print(p)
```

@@

  # PAPER CONSUMPTION
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(shape = language), size = 5) +
       geom_line(aes(linetype = language), size = 1) +       
       xlab("Publication year") +
       ylab("Paper (sheets)") +
       guides(shape = guide_legend(title = "Language")) +
       guides(linetype = guide_legend(title = "Language")) + 
       #ggtitle(paste("Temporary Sermons (", catalogue, ")", sep = ""))
       ggtitle(catalogue)       
  print(p)
```

@@

# PAPER CONSUMPTION
theme_set(theme_bw(20))
p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(shape = language), size = 5) +
       geom_line(aes(linetype = language)) +       
       xlab("Publication year") +
       ylab("Paper (sheets)") +
       guides(shape = guide_legend(title = "Language")) +
       guides(linetype = guide_legend(title = "Language")) +        
       ggtitle(catalogue)
       #ggtitle(paste("Devotional Literature (", catalogue, ")", sep = "")) 
print(p)
```
